Title: A proof-of-concept study

### 2022-01-25 paper.tex
update

\section{Introduction}
The \textit{Fermi} bubbles, two giant bubbles extending about 50 degrees above and below the Galactic center (GC),\
are among the most important findings of the Fermi Gamma-ray Space Telescope\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
  }
  \label{fig__gammaRay}
\end{figure*}

@@

%\appendix

>>>>

\section{Introduction}
A decade after the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
similar X-ray bubbles above and below the Galaxy,\
but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\

The \textit{Fermi} and eROSITA bubbles, two couple giant bubbles extending about 50 degrees\
above and below the Galactic center (GC),\
are among the most important findings of the Fermi Gamma-ray Space Telescope\

The Fermi bubbles and large-scale X-ray emission revealed by eROSITA\
show remarkable morphological similarity.

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO\
           algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
  }
  \label{fig__gammaRay}
\end{figure*}

@@

%\appendix
% https://heasarc.gsfc.nasa.gov/docs/objects/heapow/archive/normal_galaxies/fermibubbles_erosita.html

%Jet_SrcVel 0.6
%Jet_SrcDens 1e-26
%Jet_SrcTemp 2e10
%Jet_SrcPres => 1.6e-8
